---
title: "Nominal Evangelicals"
author: "Ryan Burge"
date: "June 29, 2017"
output: html_document
---

### Here are the States with the Most Nominal Evangelicals 

I used the Cooperative Clergy Election Study, 2016 to do the analysis.

The numbers you are seeing are the percent of white evangelicals who say that they attend seldom or never. 

```{r message=FALSE, warning=FALSE, echo= FALSE}
library(dplyr)
library(ggplot2)
library(extrafont)
library(leaflet)
library(viridis)
library(spdplyr)
library(haven)
library(readr)
library(car)

pulliam <- read_csv("D:/cces/pulliam.csv")
pulliam$rare <- Recode(pulliam$pew_churatd, "5:6=1; else=0")
state <- pulliam %>% filter(evangelical ==1) %>% group_by(inputstate) %>% summarise(mean = mean(rare, na.rm = TRUE))
states <- read_csv("C:/Users/Ryan Burge/Desktop/states.csv")
state <- state %>% filter(inputstate != 11)
plot <- cbind(states, state)
plot %>% arrange(-mean) %>% head(10) %>% ggplot(., aes(x=reorder(state, mean), y=mean*100, color = "dodgerblue1", fill = "black")) + geom_col() + coord_flip() +
theme(plot.title = element_text(hjust = 0.5)) + theme_minimal(base_family="Arial Narrow") + 
   theme(legend.position="none") +
  labs(x="State", y="Percent Saying Seldom or Never", 
                                                                                                   title="Evangelicals who Attend Church the Least?",
                                                                                                   subtitle="Those who say 'Seldom' or 'Never'",
                                                                                                   caption="Data from CCES 2016")

```

### Here's an Interactive Map

Brighter yellow = more nominal evangelicals. Darker greenish-blue = fewer nominal evangelicals. 

You can mouse over any state and a popup will come with the percent of evangelicals who say they attend seldom or never. 

```{r message=FALSE, warning=FALSE, echo= FALSE}

st <- rgdal::readOGR("state.json", "OGRGeoJSON")
plot$NAME <- as_factor(plot$state)
plot <- plot %>% select(NAME, mean)
plot <- plot %>% mutate(mean = round(mean*100,2))
map <- left_join(st, plot)

pal <- colorNumeric("viridis", NULL)


myLabelFormat = function(..., reverse_order = FALSE){ 
  if(reverse_order){ 
    function(type = "numeric", cuts){ 
      cuts <- sort(cuts, decreasing = T)
    } 
  }else{
    labelFormat(...)
  }
}

leaflet(map) %>%
  addTiles() %>%
  addPolygons(stroke = TRUE, weight = 1, smoothFactor = 0.3, fillOpacity = 1, color = "black",
              fillColor = ~pal(map$mean), 
              label = ~paste0(map$mean, "%"))%>%
  addLegend(pal = pal, values = rev(map$mean), opacity = 1.0, labFormat = myLabelFormat(reverse_order = F)) %>% 
  setView(-98.690940, 39.651426, zoom = 4)

```
